First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-31 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
Edit continued

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon [refs].

This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and gluons[refs to add].
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions [ref to EMC reviews]. Experimentally, the coherent DVCS channel is 
difficult to measure because of its small cross section and the necessity to
ensure that the target remains intact while emitting a hard photon 
($eA \rightarrow e' A' \gamma$). Figure \ref{fig:diags} illustrates the 
hand bag diagram for the coherent DVCS on $^4$He.

@@

Similarly to the proton case, at large photon's 4-momentum square  
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
(p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and is calculable with perturbative QED, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.

The GPDs are defined for each quark flavor and gluon as matrix
elements of the light cone operators \cite{Belitsky}, describing the transition 
between the initial and final states of a hadron. The GPDs depend on two 
longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
of the parton involved in the process and $\xi$ is the longitudinal fraction of 
the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
measured experimentally in a DVCS reaction. Hence, we measure the their 
convolutions on $x$, the so-called Compton Form Factors (CFF) 
\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.

@@

This work presents the first exclusive measurement of the beam-spin asymmetry 
of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$.This DVCS sensitive 
observable is measurable using a polarized lepton beam on an unpolarized target 
(U). It is convenient to use the beam-spin asymmetry as a DVCS observable 
because most of the experimental normalization and acceptance issues cancel out 
in the asymmetry ratio. It is defined in terms of the cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, the DVCS 
reaction is indistinguishable from the Bethe-Heitler (BH) process, where the 
final photon is emitted either from the incoming or the outgoing leptons. The 
BH process is not sensitive to GPDs and does not carry information about the 
partonic structure of the hadronic target, and it's amplitude is calculable 
from the well-known electromagnetic form factors.

>>>>

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon [refs].
This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and gluons[refs to add].
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions [ref to EMC reviews].

@@

Experimentally, the coherent nuclear DVCS channel is difficult to measure because of 
its small cross section and the necessity to ensure that the target remains 
intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
\ref{fig:diags} illustrates the hand bag diagram for the coherent DVCS on 
$^4$He. Similarly to the proton case, at large photon's 4-momentum square 
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ 
($= (p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and is calculable with perturbative QED, while the non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with the proton mass $M$ and 
$\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
transfered to the target, however the $x$ variable cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) [need reference] defined as: [add FORMULA for CFFs].

@@

In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.

This work presents the first exclusive measurement of the beam-spin asymmetry 
of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$. This DVCS sensitive 
observable is measurable using a polarized lepton beam on an unpolarized target 
(U). It is convenient to use the beam-spin asymmetry as a DVCS observable 
because most of the experimental normalization and acceptance issues cancel out 
in the asymmetry ratio. It is defined in terms of the cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, the DVCS 
reaction is indistinguishable from the Bethe-Heitler (BH) process, where the 
final photon is emitted either from the incoming or the outgoing leptons. The 
BH process is not sensitive to GPDs and does not carry information about the 
partonic structure of the hadronic target, and it's amplitude is calculable 
from the well-known electromagnetic form factors.
